refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-14 paper/manuscript.tex
PAPER: minor mod to final paragraph

Moreover, there are important ramifications for verifiability \cite{Chirigati2013}. \refnx\ is based on a fully open software stack, with good unit test coverage. The user can run tests for each component and inspect parts for correctness. For example, the behaviour of the reflectivity calculation in \refnx\ is checked from first principles in the test suite; and can be done now and in several years time. If problems are discovered, they can be corrected. With a closed source program such checking is harder, one has to examine the inputs/outputs of a black box without knowing what is happening in between, making it harder to find errors; one has to rely on trust. Whilst this may not be an issue for relatively simple calculations, it may be for complex algorithms, such as those involved with minimisation.

>>>>

Moreover, there are important ramifications for verifiability \cite{Chirigati2013}. \refnx\ is based on a fully open software stack, with good unit test coverage. The user can run tests for each component and inspect parts for correctness. For example, the behaviour of the reflectivity calculation in \refnx\ is checked from first principles in the test suite; and can be done now and in several years time. If problems are discovered, they can be corrected. With a fully or partially closed-source program such checking is much harder, as one does not possess full knowledge of what happens inside.
